
---
title: "A-Malik03: Module 4 Challenges"
subtitle: "Assignment Due 09-17-2023"
author: "Allister Malik"
output: 
  html_document:
    theme: cerulean 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Peer Commentary

Two things that I like about your code: I like that you were able to make your chunk names aka category names match the title font in the HTML file. I also like that you were able to find an easier way to extrac every third element in challenge 3 as I had to extract them individually. 

One thing that I did not like about your code is that once you created a matrix of numbers in challenge 2, you did not add a code to view it in its original state before making changes to it. 

To comment on your reflections section: I also had major issues knitting the file! Challenge 1-3 were OKAY for me, while challenge 4 and 5 took a while for me to figure out. I had issues in every challenge and had to also google/read the textbooks to try and trouble shoot. 

Overall, great job. Your code worked when I ran it, and the HTML file looks great!

-Lillian


**Reflection**  

Three difficult things were doing challenge 1, challenge 5 and getting this file to Knit. Challenge 1 was difficult because the strplit function was still returning the full vector. After figuring out the difference between this vector with other vectors using the class function, I figured I had to unlist it. And it worked! 

Challenge 5 was difficult because I could not convert the data frame columns to the desired system, it would only display as a result of inputing the code. I did some internet searching and discovered the sapply function and used that to convert the dataframe into the respective values.

Knitting this file was an unsurmountable problem I had. The terminal kept outputting "Error in yaml::yaml.load(..., eval.expr = TRUE) : /     Scanner error: while scanning a simple key at line 5, column 1 could not find expected ':' at line 6, column 1." Line 5 and line 5 coded the date and the author YAML. I created a scrap Rmarkdown to figure out the problem but I could not. In the end I decided to delete the date line, which fixed the entire problem.

This module had its difficulties but the internet was an invaluable for figuring the problems out.

**Peer Commentary Reflection**
 
Lillian's comments and seeing her code really help me understand how to use some of the functions introduced in Module 4. Additionally, after changing my code for Challenge 1, I encountered the same issue she did with not having the stringr package loaded into the file (although I am confused on why it worked with my original code). Thanks to Lillian's reflection I was able to quickly resolve the issue. She also commented on ways I could have fewer, and more efficient lines of code like reducing the number of variables and simplifying the functions I used. I agreed on the comment on displaying variable m3 in Challenge 5. I believe it's important to show the variable assigned orginally so others can understand the alterations done to them.

 
 
 
 
```{r}
library(stringr)
```


## Challenge 1
```{r,} 
u1 <- c("Stately,", "plump", "Buck", "Mulligan", "came", "from", "the", "stairhead", "bearing", "a", "bowl", "of", "lather", "on", "which", "a", "mirror", "and", "a", "razor", "lay", "crossed.")
str_split(u1, "plump", n = 1, simplify = FALSE)
u1[c(3, 6, 9, 12, 15, 18, 21)]
```

## Challenge 2
```{r}
m <- matrix(data = 1:80, nrow = 8, ncol = 10, byrow = FALSE)
m
x <- m[, c(2, 3, 6)]
x
x <- m[6:8, ]
x
x <- m[2:6, 2:9]
x
```


## Challenge 3
```{r}
a <- array(data = 400:1, dim = c(5, 5, 4, 4))
a
a[1, 1, 1, 2]
a[2, 3, 2, ]
a[1:5, 1:5, 3, 3]
```


## Challenge 4 
```{r,}
Lemuroidea <- c("Cheirogaleidae", "Lepilemuridae", "Indriidae", "Lemuridae",
    "Daubentoniidae")
Lorisoidea <- c("Lorisidae", "Galagidae")
Strepsirhini <- list(Lemuroidea, Lorisoidea)
names(Strepsirhini) <- list("Lemuroidea", "Lorisoidea")
Strepsirhini
Tarsioidea <- c("Tarsiidae")
Catarrhini <- c("Cercopithecidae", "Hylobatidae", "Hominidae")
Platyrrhini <- c("Cebidae", "Atelidae", "Pitheciidae")
Anthropoidea <- list(Platyrrhini, Catarrhini)
names(Anthropoidea) <- list("Platyrrhini", "Catarrhini")
Haplorhini <- list(Anthropoidea, Tarsioidea)
names(Haplorhini) <- list("Anthropoidea", "Tarsioidea")
Haplorhini
Primates <- list(Haplorhini, Strepsirhini)
names(Primates) <- list("Haplorhini", "Strepsirhini")
PrimatesList <- list(Primates)
names(PrimatesList) <- "Primates"
PrimatesList
```


## Challenge 5 
```{r}  
m3 <- matrix(data = c(3, 0, 1, 23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2), nrow = 5, ncol = 3, byrow = TRUE)
m3
df <- as.data.frame(m3)
df
df[, 2] <- as.logical(df[, 2])
df[, 3] <- as.factor(df[, 3])
df
str(df)
```
<center>THE END. . .<center> 