---
title: "A-Malik03: Module 4 Challenges"
subtitle: "Assignment Due 09-17-2023"
author: "Allister Malik"
output: 
  html_document:
    theme: cerulean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




**Reflection**  

Three difficult things were doing challenge 1, challenge 5 and getting this file to Knit. Challenge 1 was difficult because the strplit function was still returning the full vector. After figuring out the difference between this vector with other vectors using the class function, I figured I had to unlist it. And it worked! 

Challenge 5 was difficult because I could not convert the dataframe columns to the desired system, it would onyl desplay as a result of inputing the code. I did some internet searching and discovered the sapply function and used that to convert the dataframe into the respective values.

Knitting this file was an unsurmountable problem I had. The terminal kept outputing "Error in yaml::yaml.load(..., eval.expr = TRUE) : /     Scanner error: while scanning a simple key at line 5, column 1 could not find expected ':' at line 6, column 1." Line 5 and line 5 coded the date and the author YAML. I created a scrap Rmarkdown to figure out the problem but I could not. In the end I decided to delete the date line, which fixed the entire problem.

This module had its difficulties but the internet was an invaluable for figuring the problems out.

## Challenge 1
```{r,}
u1 <- "Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed."
u2 <- unlist(strsplit(u1, split = " "))
u2[seq(0, length(u2), 3)]
```

## Challenge 2
```{r}
m <- matrix(data = 1:80, nrow = 8, ncol = 10, byrow = FALSE)
x <- m[, c(2, 3, 6)]
x
x <- m[6:8, ]
x
x <- m[2:6, 2:9]
x
```


## Challenge 3
```{r}
a <- array(data = 400:1, dim = c(5, 5, 4, 4))
a
a[1, 1, 1, 2]
a[2, 3, 2, ]
a[1:5, 1:5, 3, 3]
```


## Challenge 4
```{r,}
Lemuroidea <- c("Cheirogaleidae", "Lepilemuridae", "Indriidae", "Lemuridae",
    "Daubentoniidae")
Lorisoidea <- c("Lorisidae", "Galagidae")
Strepsirhini <- list(Lemuroidea, Lorisoidea)
names(Strepsirhini) <- list("Lemuroidea", "Lorisoidea")
Strepsirhini
Tarsioidea <- c("Tarsiidae")
Catarrhini <- c("Cercopithecidae", "Hylobatidae", "Hominidae")
Platyrrhini <- c("Cebidae", "Atelidae", "Pitheciidae")
Anthropoidea <- list(Platyrrhini, Catarrhini)
names(Anthropoidea) <- list("Platyrrhini", "Catarrhini")
Haplorhini <- list(Anthropoidea, Tarsioidea)
names(Haplorhini) <- list("Anthropoidea", "Tarsioidea")
Haplorhini
Primates <- list(Haplorhini, Strepsirhini)
names(Primates) <- list("Haplorhini", "Strepsirhini")
PrimatesList <- list(Primates)
names(PrimatesList) <- "Primates"
PrimatesList
```


## Challenge 5
```{r}
m3 <- matrix(data = c(3, 0, 1, 23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2), nrow = 5, ncol = 3, byrow = TRUE)
m3
df <- as.data.frame(m3)
df[, 2] <- sapply(df[,2], as.logical)
df[, 3] <- sapply(df[, 3], as.factor)
print.data.frame(df)
str(df)
```
<center>THE END. . .<center>


